### 2018-07-29 cover-letter/cover-letter.tex
Conclusion and discussion section finished
Graph abstract, cover letter and highlighs finished

Please find enclosed a manuscript entitled: ``Modeling and Simulation of Online
Reprocessing in the Thorium-Fuelled Molten Salt Breeder Reactor'' which Mr. 
Andrei Rykhlevskii and I are submitting for exclusive consideration of 
publication as a research article in Annals of Nuclear Energy.

>>>>

Please find enclosed a manuscript entitled: ``Modeling and Simulation of Online
Reprocessing in the Thorium-Fueled Molten Salt Breeder Reactor'' which Mr. 
Andrei Rykhlevskii, Mr. Jin Whan Bae and I are submitting for exclusive consideration of 
publication as a research article in Annals of Nuclear Energy.

### 2018-07-29 introduction.tex
Graph abstract, cover letter and highlighs finished

\begin{table}[ht!]
\caption{Tools and methods for fast spectrum system fuel cycle analysis.}
\begin{tabularx}{\textwidth}{ x | s | s | m | x } 
\# & Neutronic code  & Depletion code    & \qquad Authors & Spectra   \\
\hline
1 & \gls{MCNP} \cite{noauthor_mcnp_2004}      & REM \cite{heuer_simulation_2010}  & Doligez \emph{et al.}, 2014; Heuer \emph{et al.}, 2014  \cite{doligez_coupled_2014,heuer_towards_2014}    & fast \\
\hline
2 & ERANOS \cite{ruggieri_eranos_2006}      & ERANOS     & Fiorina \emph{et al.}, 2013 \cite{fiorina_investigation_2013}            & fast \\
\hline
3 & KENO-IV \cite{goluoglu_monte_2011}     & ORIGEN \cite{gauld_isotopic_2011}     & Sheu \emph{et al.}, 2013 \cite{sheu_depletion_2013} & fast \\
\hline
4 & SERPENT 2 \cite{leppanen_serpent_2015}   & SERPENT 2  & Aufiero \emph{et al.}, 2013 \cite{aufiero_extended_2013} & fast \\
\hline
5 & MCODE \cite{xu_mcode_2008}      & ORIGEN2 \cite{croff_users_1980}      & Ahmad \emph{et al.}, 2015 \cite{ahmad_neutronics_2015}   & thermal  \\
\hline
6 & \gls{MCNP}6     & CINDER90 \cite{goorley_mcnp6_2013}     & Park \emph{et al.}, 2015; Jeong \emph{et al.}, 2016 \cite{park_whole_2015, jeong_equilibrium_2016}& thermal\\
\hline
7 & SCALE \cite{bowman_scale_2011}      & SCALE/ ChemTriton \cite{powers_new_2013}    & Powers \emph{et al.}, 2014; Betzler \emph{et al.}, 2017 \cite{powers_new_2013,powers_inventory_2014,betzler_molten_2017}& thermal\\
\hline
8 & SERPENT 2      & SERPENT 2     & Rykhlevskii \emph{et al.}, 2017 \cite{rykhlevskii_online_2017} & thermal\\
\hline
9 & \gls{MCNP}      & REM  & Nuttin \emph{et al.} \cite{nuttin_potential_2005}&thermal  \\
\end{tabularx}
  \label{tab:fs_codes}
\end{table}
\FloatBarrier

@@

The present work introduces the online reprocessing simulation code, SaltProc, which expands the capability of the continuous-energy Monte Carlo Burnup calculation code, SERPENT 2 \cite{leppanen_serpent_2015}, for simulation liquid-fueled \gls{MSR} operation \cite{andrei_rykhlevskii_arfc/saltproc:_2018}. It is also reports the application of the coupled SaltProc-SERPENT 2 system to the \gls{MSBR}, which represents the continuation of the work presented in \cite{rykhlevskii_full-core_2017, rykhlevskii_online_2017}. The major objective of the work herein is to analyze \gls{MSBR} neutronics and fuel cycle to find the equilibrium core composition and core depletion. The additional objective is to compare predicted operational and safety parameters of the \gls{MSBR} at both the initial and equilibrium states. Finally, $^{232}$Th feed rate will be determined and \gls{MSBR} fuel cycle performance will be analyzed.

>>>>

\begin{table}[ht!]
\caption{Tools and methods for fast spectrum system fuel cycle analysis.}
\begin{tabularx}{\textwidth}{ x | s | s | m | x } 
\hline & Neutronic code  & Depletion code    & \qquad Authors & Spectra   \\
\hline
1 & \gls{MCNP} \cite{noauthor_mcnp_2004}      & REM \cite{heuer_simulation_2010}  & Doligez \emph{et al.}, 2014; Heuer \emph{et al.}, 2014  \cite{doligez_coupled_2014,heuer_towards_2014}    & fast \\
\hline
2 & ERANOS \cite{ruggieri_eranos_2006}      & ERANOS     & Fiorina \emph{et al.}, 2013 \cite{fiorina_investigation_2013}            & fast \\
\hline
3 & KENO-IV \cite{goluoglu_monte_2011}     & ORIGEN \cite{gauld_isotopic_2011}     & Sheu \emph{et al.}, 2013 \cite{sheu_depletion_2013} & fast \\
\hline
4 & SERPENT 2 \cite{leppanen_serpent_2015-1}   & SERPENT 2  & Aufiero \emph{et al.}, 2013 \cite{aufiero_extended_2013} & fast \\
\hline
5 & MCODE \cite{xu_mcode_2008}      & ORIGEN2 \cite{croff_users_1980}      & Ahmad \emph{et al.}, 2015 \cite{ahmad_neutronics_2015}   & thermal  \\
\hline
6 & \gls{MCNP}6     & CINDER90 \cite{goorley_mcnp6_2013}     & Park \emph{et al.}, 2015; Jeong \emph{et al.}, 2016 \cite{park_whole_2015, jeong_equilibrium_2016}& thermal\\
\hline
7 & SCALE \cite{bowman_scale_2011}      & SCALE/ ChemTriton \cite{powers_new_2013}    & Powers \emph{et al.}, 2014; Betzler \emph{et al.}, 2017 \cite{powers_new_2013,powers_inventory_2014,betzler_molten_2017}& thermal\\
\hline
8 & SERPENT 2      & SERPENT 2     & Rykhlevskii \emph{et al.}, 2017 \cite{rykhlevskii_online_2017} & thermal\\
\hline
9 & \gls{MCNP}      & REM  & Nuttin \emph{et al.} \cite{nuttin_potential_2005}&thermal  \\ \hline
\end{tabularx}
  \label{tab:fs_codes}
\end{table}
\FloatBarrier

@@

The present work introduces the online reprocessing simulation code, SaltProc, which expands the capability of the continuous-energy Monte Carlo Burnup calculation code, SERPENT 2 \cite{leppanen_serpent_2015-1}, for simulation liquid-fueled \gls{MSR} operation \cite{andrei_rykhlevskii_arfc/saltproc:_2018}. It is also reports the application of the coupled SaltProc-SERPENT 2 system to the \gls{MSBR}, which represents the continuation of the work presented in \cite{rykhlevskii_full-core_2017, rykhlevskii_online_2017}. The major objective of the work herein is to analyze \gls{MSBR} neutronics and fuel cycle to find the equilibrium core composition and core depletion. The additional objective is to compare predicted operational and safety parameters of the \gls{MSBR} at both the initial and equilibrium states. Finally, $^{232}$Th feed rate will be determined and \gls{MSBR} fuel cycle performance will be analyzed.
